Symmetric Circuits for Rank Gates

### 2018-04-02 sections/transparency-and-unique-extensions.tex
I made major changes to the transparency section. I fixed a few typos in the symmetric circuits section.

\begin{lem}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a $(\BB,
  \rho)$-circuit of order $n$ and $C_{\equiv} = \langle G_\equiv ,
  \Omega_\equiv, \Sigma_\equiv , \Lambda_\equiv, L_\equiv \rangle$ be a quotient
  of $C$. Then $C_\equiv$ is reduced and $C$ and $C_{\equiv}$ compute the same
  function. Moreover, if $C$ is symmetric then $C_{\equiv}$ is symmetric, and
  for all $g \in G$, $g$ has unique labels in $C$ if, and only if, $[g]$ has
  unique labels in $C_{\equiv}$.
  \label{lem:quotient-circuits-preserve}
\end{lem}
\begin{proof}
  We first prove that $C_\equiv$ and $C$ compute the same function. Let
  $\mathcal{A}$ be a $\rho$-structure of size $n$ and let $\gamma$ be a
  bijection from $U$ to $[n]$. We now show that for all $g \in G$, $C_\equiv
  [\gamma \mathcal{A}]([g]) = C[\gamma \mathcal{A}](g)$. We do this by induction
  on the depth of a gate. Suppose $g \in G$ has depth $0$. In this case $g$ is
  an input gate and the result follows trivially. Suppose $g$ is an internal
  gate and suppose for all $h$ of depth less than $g$ we have that
  $C_\equiv[\gamma \mathcal{A}]([h]) = C[\gamma \mathcal{A}](h)$. We have that
  there exists $g' \in [g]$ such that $L_\equiv ([g]) = L(g') /_\equiv$ and
  $\Sigma_\equiv([g]) = \Sigma (g) = \Sigma (g')$. We have from
  Lemma~\ref{lem:syntactic-equivalence-equal-function} and the inductive
  hypothesis that there exists $\lambda \in \aut(g)$ such that $L_\equiv ([g]) =
  L(g') = L(g) \lambda$. It follows from the fact that $\Sigma(g)$ is a
  structured function that $C_\equiv[\gamma \mathcal{A}]([g]) = \Sigma_\equiv
  ([g])(L^{\gamma \mathcal{A}}_\equiv([g])) = \Sigma (g') (L^{\gamma
    \mathcal{A}}(g')) = \Sigma (g)(L^{\gamma \mathcal{A}}(g) \lambda) = \Sigma
  (g) (L^{\gamma \mathcal{A}}(g)) = C[\gamma \mathcal{A}](g)$.

@@

  We now show that if $C$ is symmetric then $C_\equiv$ is symmetric. Suppose $C$
  is symmetric. Let $\sigma \in \sym_n$. Then there exists $\pi \in \aut(C)$
  that extends $\sigma$. Let $\pi_\equiv = pi /_\equiv$. We now show that
  $\pi_\equiv$ is an automorphism of $C_\equiv$ extending $\sigma$. It is easy
  to see that $\pi_\equiv$ is a bijection from $G_\equiv$ to $G_\equiv$ that
  preserves syntactic-equivalence, and is thus is a well-defined function. Let
  $[g] \in G_\equiv$. We have that $\Sigma_\equiv (\pi_\equiv [g]) =
  \Sigma_\equiv ([\pi g]) = \Sigma (\pi g) = \Sigma (g) = \Sigma_\equiv ([g])$.
  It is easy to check the automorphism conditions for input gates. Suppose $[g]$
  is an internal gate. Let $g' \in [g]$ be such that $L_\equiv([g]) = L(g')
  /_\equiv$ and $h \in [g]$ be such that $L_\equiv(\pi_\equiv[g]) = L_\equiv
  ([\pi h]) = L(\pi h) /_\equiv$. We have that $\pi L(g')$ is
  isomorphism-equivalent to $L(\pi g')$, and it follows that $(\pi
  L(g'))/_\equiv$ is isomorphism-equivalent to $L(\pi g') /_\equiv$. We then
  have $(\pi L(g'))/_\equiv = \pi_\equiv (L(g') /_\equiv) = \pi_\equiv L_\equiv
  ([g])$ and, since $g' \equiv h$ and so $\pi g' \equiv \pi h$, we have that
  $L(\pi g')/_\equiv$ is isomorphism-equivalent to $L(\pi h) /_\equiv =
  L_\equiv(\pi_\equiv[g])$. It follows that $\pi_\equiv L_\equiv ([g])$ is
  isomorphism-equivalent to $L_\equiv(\pi_\equiv [g]) /_\equiv$. Suppose $[g]$
  is an output gate. Then for $\vec{a} \in \dom (\Omega)$, $\pi_\equiv
  \Omega_\equiv (\vec{a}) = [\pi \Omega (\vec{a})] = [\Omega (\sigma \vec{a})] =
  \Omega_\equiv (\sigma \vec{a})$.

@@

\begin{lem}
  There is an algorithm takes as input a $(\BB, \rho)$-circuit $C$ of order $n$
  with unique labels and $\sigma \in \sym_n$ and outputs for each gate $g$ the
  image of $g$ under the action of the unique automorphism extending $\sigma$
  (if it exists). This algorithm runs in time polynomial in the combined size of
  the input circuit and the encoding of the permutation.
  \label{lem:compute-automorphisms}
\end{lem}
\begin{proof}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$. We recursively build
  up the mapping $\pi$ extending $\sigma$. If at some point in the recursive
  construction we arrive at a point where no mapping for $g$ can be found we
  halt at that point and return that no automorphism exists.

  Let $h$ be any gate in the circuit. Suppose $h$ is an input gate. If $h$ is a
  constant gate then let $\pi (h) = h'$. If $h$ is a relational gate such that
  $R := \Sigma(h)$, then check if there exists $h'$ such that $\Sigma (h') = R$,
  $\sigma \Lambda_R(h) = \Lambda_R(h')$, and either both $h$ and $h'$ are output
  gates or neither are. If no such $h'$ exists then halt and output that no
  automorphism exists. If neither $h$ nor $h'$ are output gates then set $\pi
  (h) = h'$. If both $h$ and $h'$ are output gates then check if $\sigma
  \Omega^{-1}(h) = \Omega^{-1}(h')$. If the equality holds set $\pi(h) = h'$,
  otherwise halt and output that no automorphism exists. We have from
  Proposition~\ref{prop:unique-children-unique-extensions} that there is at most
  one gate $h'$ that meets the above criteria, and so $\pi(h)$ is well defined.

  Let $h$ be an internal gate in the circuit and assume we have defined $\pi
  (g)$ for every gate $g$ of depth less than $h$. Let $h'$ be a gate in the
  circuit such that $\Sigma(h) = \Sigma (h')$, $\pi L(h)$ is
  isomorphism-equivalent to $L(h')$ and, if $h$ is an output gate then $h'$ is
  an output gate such that $\sigma \Omega^{-1}(h) = \Omega^{-1}(h')$. Since $C$
  has unique labels (and so unique extensions) we have that $\pi L(h)$ is
  isomorphism-equivalent to $L(h')$ if, and only if, $L(h')^{-1}\pi L(h)$ acts
  on $\ind(h)$ like an automorphism of $\str{h}$. This can be determined easily.
  If no such $h'$ exists halt and output that there is no automorphism extending
  $\sigma$. Since $C$ has unique labels it has unique extensions, and so there
  is at most one such $h'$. We thus let $\pi (h) = h'$.

  This recursive approach can be implemented as an algorithm that runs in time
  polynomial in the combined size of the inputs and outputs the required
  automorphism if it exists.
\end{proof}

We now define an algorithm analogous to the one defined in
Lemma~\ref{lem:compute-automorphisms} that computes in polynomial-time the image
of a given element of the universe of a gate under the action of a given
permutation.

>>>>

\begin{lem}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a $(\BB,
  \rho)$-circuit of order $n$ and $C_{\equiv} = \langle G_\equiv ,
  \Omega_\equiv, \Sigma_\equiv , \Lambda_\equiv, L_\equiv \rangle$ be a quotient
  of $C$. Then $C_\equiv$ is reduced and $C$ and $C_{\equiv}$ compute the same
  function. Moreover, if $C$ is symmetric then $C_{\equiv}$ is symmetric, and
  for all $g \in G$, $g$ has unique labels in $C$ if, and only if, $[g]$ has
  unique labels in $C_{\equiv}$. In fact, for all $\sigma \in \sym_n$ if there
  exists $\pi \in \aut(C)$ extending $\sigma$ then $\pi /_\equiv$ is an
  automorphism of $C_\equiv$ extending $\sigma$.
  \label{lem:quotient-circuits-preserve}
\end{lem}
\begin{proof}
  We first prove that $C_\equiv$ and $C$ compute the same function. Let
  $\mathcal{A}$ be a $\rho$-structure of size $n$ and let $\gamma$ be a
  bijection from $U$ to $[n]$. We now show that for all $g \in G$, $C_\equiv
  [\gamma \mathcal{A}]([g]) = C[\gamma \mathcal{A}](g)$. We do this by induction
  on the depth of a gate. Suppose $g \in G$ has depth $0$. In this case $g$ is
  an input gate and the result follows trivially. Suppose $g$ is an internal
  gate and suppose for all $h$ of depth less than $g$ we have that
  $C_\equiv[\gamma \mathcal{A}]([h]) = C[\gamma \mathcal{A}](h)$. We have that
  there exists $g' \in [g]$ such that $L_\equiv ([g]) = L(g') /_\equiv$ and
  $\Sigma_\equiv([g]) = \Sigma (g) = \Sigma (g')$. We have from
  Lemma~\ref{lem:syntactic-equivalence-equal-function} and the inductive
  hypothesis that there exists $\lambda \in \aut(g)$ such that $L_\equiv ([g]) =
  L(g') = L(g) \lambda$. It follows from the fact that $\Sigma(g)$ is a
  structured function that $C_\equiv[\gamma \mathcal{A}]([g]) = \Sigma_\equiv
  ([g])(L^{\gamma \mathcal{A}}_\equiv([g])) = \Sigma (g') (L^{\gamma
    \mathcal{A}}(g')) = \Sigma (g)(L^{\gamma \mathcal{A}}(g) \lambda) = \Sigma
  (g) (L^{\gamma \mathcal{A}}(g)) = C[\gamma \mathcal{A}](g)$.

@@

  Let $\sigma \in \sym_n$ and suppose there exists $\pi \in \aut(C)$ extending
  $\sigma$. Let $\pi_\equiv = pi /_\equiv$. We now show that $\pi_\equiv$ is an
  automorphism of $C_\equiv$ extending $\sigma$. It is easy to see that
  $\pi_\equiv$ is a bijection from $G_\equiv$ to $G_\equiv$ that preserves
  syntactic-equivalence, and is thus is a well-defined function. Let $[g] \in
  G_\equiv$. We have that $\Sigma_\equiv (\pi_\equiv [g]) = \Sigma_\equiv ([\pi
  g]) = \Sigma (\pi g) = \Sigma (g) = \Sigma_\equiv ([g])$. It is easy to check
  the automorphism conditions for input gates. Suppose $[g]$ is an internal
  gate. Let $g' \in [g]$ be such that $L_\equiv([g]) = L(g') /_\equiv$ and $h
  \in [g]$ be such that $L_\equiv(\pi_\equiv[g]) = L_\equiv ([\pi h]) = L(\pi h)
  /_\equiv$. We have that $\pi L(g')$ is isomorphism-equivalent to $L(\pi g')$,
  and it follows that $(\pi L(g'))/_\equiv$ is isomorphism-equivalent to $L(\pi
  g') /_\equiv$. We then have $(\pi L(g'))/_\equiv = \pi_\equiv (L(g') /_\equiv)
  = \pi_\equiv L_\equiv ([g])$ and, since $g' \equiv h$ and so $\pi g' \equiv
  \pi h$, we have that $L(\pi g')/_\equiv$ is isomorphism-equivalent to $L(\pi
  h) /_\equiv = L_\equiv(\pi_\equiv[g])$. It follows that $\pi_\equiv L_\equiv
  ([g])$ is isomorphism-equivalent to $L_\equiv(\pi_\equiv [g]) /_\equiv$.
  Suppose $[g]$ is an output gate. Then for $\vec{a} \in \dom (\Omega)$,
  $\pi_\equiv \Omega_\equiv (\vec{a}) = [\pi \Omega (\vec{a})] = [\Omega (\sigma
  \vec{a})] = \Omega_\equiv (\sigma \vec{a})$. It follows that if $C$ is
  symmetric then $C_\equiv$ is symmetric.

@@

% \begin{lem}
%   There is an algorithm that takes as an input a circuit $C$ of order $n$
% \end{lem}

% \begin{lem}
%   There is an algorithm takes as input a $(\BB, \rho)$-circuit $C$ of order
%   $n$ with unique labels and $\sigma \in \sym_n$ and outputs for each gate $g$
%   the image of $g$ under the action of the unique automorphism extending
%   $\sigma$ (if it exists). This algorithm runs in time polynomial in the
%   combined size of the input circuit and the encoding of the permutation.
%   \label{lem:compute-automorphisms}
% \end{lem}
% \begin{proof}
%   Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$. We first construct
%   a circuit $C^\sigma$ from $C$ by adding in the image of each gate in $C$
%   under the action of $\sigma$. We now define this circuit formally.

%   Let $C^\sigma := \langle G^\sigma, \Omega^\sigma, \Sigma^\sigma,
%   \Lambda^\sigma, L^\sigma \rangle$. For each internal gate $g$ in $G$ we
%   define a new gate $g^\sigma$ and let $G'$ be the set of all of these new
%   gates. Let $G^\sigma = G \ucup G'$. Let $\Lambda^\sigma = \Lambda$ and
%   $\Omega^\sigma = \Omega$. Let $\Sigma^\sigma (g) = \Sigma(g)$ for all $g \in
%   G$ and $\Sigma^\sigma (g^\sigma) = \Sigma (g)$ for all $g^\sigma \in G'$.
%   For each $g \in G$ let $L^\sigma(g) = L(g)$. For each $g^\sigma \in G'$ and
%   $x \in \ind(g^\sigma)$ let $h = L(g)(x)$. If $h$ is an input gate then there
%   is an obvious action of $\sigma$ on $h$ and we let $L^\sigma(g^\sigma)(x) =
%   \sigma h$. If $h$ is an internal gate there there exists $h^\sigma \in G'$
%   and we let $L^\sigma(g^\sigma)(x) = h^\sigma$.

%   We should note that $C^{\sigma}$ does have redundant gates. Let $E, E'
%   \subseteq {G^{\sigma}}^2$ be an equivalence relation defined as follows. Let
%   $(g, g') \in E'$ if, and only if, $g,g' \in G$ and $g \equiv g'$ or there
%   exists $h, h' \in G$ such that $g = h^\sigma$ and $g' = {h'}^\sigma$, and $h
%   \equiv h'$. Let $(g,g') \in E$ if, and only if, $(g, g') \in E'$ or

%   Let $g, g' \in G^{\sigma}$. If $g, g' \in G$ then $g \equiv g'$ if, and only
%   if,$E(g,g')$, and if $g, g' \in G'$ then $E(g, g')$ if

%   It is easy to see that $C^\sigma$ has unique labels and $\vert C^\sigma
%   \vert \leq \vert C \vert$. We may thus use the algorithm from Lemma~\ref{}
%   to compute the syntactic-equivalence classes of $C^\sigma$. We now have the
%   following claim.

%   \begin{claim}
%     Let $\pi \in \aut(C)$ extending $\sigma$. If $g$ and $g'$ are internal
%     non-output gates in $C$ and $g' = \pi (g)$ then $g'$ and $g^\sigma$ are
%     syntactically-equivalent in $C^\sigma$.
%   \end{claim}
%   \begin{proof}
%     We prove this claim by induction on the depth of a gate in the circuit.
%     Let $g$ and $g'$ be internal non-output gates in $C$ and $g' = \pi (g)$.
%     Suppose $g$ and $g'$ have depth $1$ i n $C$. It is clear that both $g$ and
%     $g'$ are non-output internal gates, that $\Sigma (g) = \Sigma (g')$, and
%     that there exists $\lambda \in \aut(g)$ such that $\pi L(g) = L(g')
%     \lambda$. But, since $g$ and $g'$ have depth $1$ and so all of their
%     children are input gates, we have for all $x \in \ind(g)$, that
%     $L^\sigma(g^\sigma)(x) = \pi L(g)(x) = L(g') \lambda = L^\sigma(g')
%     \lambda$. It follows that $g^\sigma$ and $g'$ are syntactically-equivalent
%     in $C^\sigma$.

%     Suppose $g$ and $g'$ have depth $i > 1$ and the result holds for all pairs
%     of gates of depth less than $i$. It follows that there exists $\lambda \in
%     \aut(g)$ such that $\pi L(g) = L(g') \lambda$. Let $x \in \ind(g)$ and let
%     $h = L(g)(x)$. If $h$ is an input gate then $L^\sigma(g^\sigma)(x) = \pi
%     L(g)(x) = L(g')(\lambda x) = L^\sigma(g')(\lambda x)$. If $h$ is not an
%     input gate then $L^\sigma (g^\sigma)(x) = h^\sigma$. We have that $\pi (h)
%     = \pi L(g)(x) = L(g')(\lambda x)$ and, from the inductive hypothesis, we
%     have that $\pi(h)$ is syntactically-equivalent to $h^\sigma$ in
%     $C^\sigma$. But then $L^\sigma (g^\sigma)(x) = h^\sigma \equiv \pi(h) =
%     L(g')(\lambda x) = L^\sigma(g')(\lambda x)$. The claim follows.
%   \end{proof}

%   each point in this construction, when extending the mapping by a single
%   gate, we notice that in each case there is only one choice of possible
%   gate.If at some point in the recursive construction we arrive at a point
%   where no mapping for $h$ can be found we halt at that point and return that
%   no automorphism exists.

%   For each gate $h$ in $C$ let $Q(h)$ be the maximum length of a path from $h$
%   to an output gate. Let $h$ be a gate in $C$. Suppose $Q(h) = 0$. Then $h$ is
%   an output gate. We recall that $\Omega$ is an injection. Let $\vec{a} =
%   \Omega^{-1}(g)$ and let $h' \in G$ be such that $h' = \Omega (\sigma
%   \vec{a})$ and $\Sigma (h) = \Sigma (h')$. Let $\pi (h) = h'$. Note that
%   there is no other partial-automorphism extending $\sigma$ on the output
%   gates of $C$, so if at this point we have failed to construct $\pi$ then
%   there is indeed no automorphism extending of $\sigma$.

%   Suppose $h$ is a gate in the circuit with $Q(h) > 0$ and for all $g$ with
%   $Q(g ) < Q(h)$ we have defined $\pi (g)$ and that $\pi$ is a partial
%   automorphism extending $\sigma$. Let $H = \bigcap_{g \in W(h, \cdot)}
%   H_{\pi(g)}$. Notice that if there is an automorphism extending $\sigma$ then
%   the image of $h$ under the action of that automorphism is in $H$. As such,
%   if $H$ is empty we halt and output that no extension exists. Suppose that
%   $H$ is non-empty. If $h$ is an input gate then there is an obvious action of
%   $\sigma$ on $h$, and we let $h' = \sigma h$. If $h$ is an output gate, let
%   $\vec{a} = \Omega^{-1}(g)$ and let $h' \in G$ be such that $h' = \Omega
%   (\sigma \vec{a})$ and $\Sigma (h) = \Sigma (h')$. If $h' \not\in H$ we halt
%   and output that no extension exists, and otherwise we let $\pi (h) = h'$.
%   Notice that in the case that $h$ is an output gate or an input gate there is
%   at most one choice of $h'$. Suppose $h$ is an internal non-output gate. Let
%   $h' \in H$ such that $h'$ is syntactically-equivalent to $h^\sigma$ in
%   $C^\sigma$. If not such $h'$ exists then, from the claim, there is no
%   extension of $\sigma$ to an automorphism of the circuit, and so we halt and
%   output accordingly. Suppose that $h'$ does exist. We now show that $h'$ is
%   unique. Let $h'' \in H$ such that $h''$ is syntactically-equivalent to
%   $h^\sigma$ in $C^\sigma$. It follows that there exists $g \in W(h, \cdot)$
%   such that $h', h'' \in H_g$ and $g$ has unique labels. Moreover, $h'$ and
%   $h''$ are syntactically-equivalent in $C^\sigma$ and so, from the
%   construction of $C^\sigma$, $h'$ and $h''$ are syntactically-equivalent in
%   $C$. But then $h' \equiv h''$ and so, since $g$ has unique labels, $h' =
%   h''$. Let $\pi (h) = h'$. Notice that in each case there is at most one
%   possible extension of $\pi$ to $h$.

%   \begin{claim}
%     There is an automorphism extending $\sigma$ if, and only if, $\pi$ is an
%     automorphism extending $\sigma$.
%   \end{claim}
%   \begin{proof}
%     `$\Rightarrow$': trivial `$\Leftarrowrrow$' : Let $\pi'$ be an
%     automorphism extending $\sigma$. We show by induction on the structure of
%     the circuit that for all $h \in G$, $\pi'(h) = \pi(h)$. Let $h \in G$. If
%     $Q(h) = 0$ then $h$ is an output gate. Let $\vec{a} = \Omega(h)$. We have
%     from the definition of $\pi$ and the definition of an automorphism that
%     $\pi(h) = \Omega(\sigma \vec{a}) = \pi'(\Omega(\vec{a})) = \pi' (h)$.

%     Suppose $Q(h) > 0 $ and for all gates $g \in G$ with $Q(g) < Q(h)$, $\pi
%     (g) = \pi'(g)$. If $h$ is an output gate then the above argument suffices
%     to show that $\pi(h) = \pi'(h)$. If $h$ is is easy to see that $\pi (g) =
%     \pi'(g)$. Suppose that $h$ is a non-output internal gate. We have from the
%     previous claim that $\pi'(h)$ is syntactically-equivalent to $h^\sigma$ in
%     $C^\sigma$. We already have that $\pi(h)$ is syntactically-equivalent to
%     $h^\sigma$. It follows that $\pi (h)$ and $\pi'(h)$ are
%     syntactically-equivalent. Let $g \in W(h, \cdot)$. We have that $\pi(h)
%     \in H_{\pi(g)}$ and $\pi'(h) \in H_{\pi'(g)}$. From the inductive
%     hypothesis $\pi (g) = \pi'(g)$, and so $\pi' (h) \in H_{\pi(g)}$. But
%     $\pi(g)$ has unique labels and $\pi(h)$ and $\pi'(h)$ are
%     syntactically-equivalent. It follows that $\pi (h) = \pi'(h)$.
%   \end{proof}

%   It remains to check that $\pi$ is an automorphism extending $\sigma$. It
%   suffices to check that for each $g \in G$, there exists $\lambda \in
%   \aut(C)$ such that $\pi L(g) = L(\pi g) \lambda$. But this is equivalent to
%   testing if for each $g \in G$, $L(\pi g) \pi L(g)^{-1}$ acts like an
%   automorphism. This is easy to check. We check if $\Sigma (h) = \Sigma (h')$
%   and check that both

%   If there is no such $h'$ then either $\bigcap_{g \in W(h, \cdot)}
%   H_{\pi(g)}$ is empty or it is non-empty but th

%   $g' \in W(\pi(h), \cdot)$

%   (g)(x) = \$

%   Then for all $x \in \ind(g)$, $L(g)(x)$

%   We should note that $C^\pi$ has unique labels.

%   Let $C_0 = C$. Let $i \in [\depth(g)]$. Let $C_i := \langle G_i, \Omega_i,
%   \Sigma_i, \Lambda_i, L_i\rangle$ be defined from $C_{i-1} := \langle
%   G_{i-1}, \Omega_{i-1}, \Sigma_{i-1}, \Lambda_{i-1}, L_{i-1} \rangle$ as
%   follows. For each internal gate $h \in G$ such that $\depth(h) = i$ and
%   either $W_T(h,g)$ or $h = g$ we define a new gate $h^\pi$. Let $G_i'$ be the
%   set of all these new gates and let $G_i = G_{i-1} \uplus G_i'$. Let
%   $\Omega_i = \Omega_{i-1}$ and $\Lambda_i = \Lambda_{i-1}$. Let $h' \in G_i$.
%   If $h' \in G_{i-1}$ then $\Sigma_i(h') = \Sigma_{i-1}(h')$ and $L_i(h') =
%   L_{i-1}(h')$. If $h' \not\in G_i$ then $h' \in G_i'$ and so $h' = h^\pi$ for
%   some appropriate $h \in G$. Let $\Sigma_i(h') = \Sigma_{i-1} (h)$. Let $x
%   \in \ind(h')$ and let $h_x := L(h)(x)$. If $h_x$ is an input gate let
%   $L(h')(x) = \sigma L(h)(x)$. Otherwise, $h_x$ is an internal gate and,
%   moreover, $W_T(h_x,g)$ and the depth of $h_x$ is less than $i$. We thus have
%   that there exists $h^\pi_x \in G_i$ corresponding to $h^\pi_x$.

%   \begin{claim}
%     For each $g' \in W(\cdot, \pi(h))$, $g'$ is the image of $g$ under the
%     action of $\sigma$ if, and only if, $g'$ is syntactically-equivalent to
%     $g^\pi$ in $C_g$.
%   \end{claim}
%   \begin{proof}
%   \end{proof}
%   Let $L(h')(x) = h^{\pi}_x$.

%   Let $C_g = C_{\depth(g)}$. Let

%   otherwise let $L(h')(x) = h^\pi_x$.

%   $L(h')(x) =.

%   let $g_h' = L(h)^{-1}(g)$

%   Let $h$ be any gate in the circuit. Suppose $h$ is an input gate. If $h$ is
%   a constant gate then let $\pi (h) = h'$. If $h$ is a relational gate such
%   that $R := \Sigma(h)$, then check if there exists $h'$ such that $\Sigma
%   (h') = R$, $\sigma \Lambda_R(h) = \Lambda_R(h')$, and either both $h$ and
%   $h'$ are output gates or neither are. If no such $h'$ exists then halt and
%   output that no automorphism exists. If neither $h$ nor $h'$ are output gates
%   then set $\pi (h) = h'$. If both $h$ and $h'$ are output gates then check if
%   $\sigma \Omega^{-1}(h) = \Omega^{-1}(h')$. If the equality holds set $\pi(h)
%   = h'$, otherwise halt and output that no automorphism exists. We have from
%   Proposition~\ref{prop:unique-children-unique-extensions} that there is at
%   most one gate $h'$ that meets the above criteria, and so $\pi(h)$ is well
%   defined.

%   Let $h$ be an internal gate in the circuit and assume we have defined $\pi
%   (g)$ for every gate $g$ of depth less than $h$. Let $h'$ be a gate in the
%   circuit such that $\Sigma(h) = \Sigma (h')$, $\pi L(h)$ is
%   isomorphism-equivalent to $L(h')$ and, if $h$ is an output gate then $h'$ is
%   an output gate such that $\sigma \Omega^{-1}(h) = \Omega^{-1}(h')$. Since
%   $C$ has unique labels (and so unique extensions) we have that $\pi L(h)$ is
%   isomorphism-equivalent to $L(h')$ if, and only if, $L(h')^{-1}\pi L(h)$ acts
%   on $\ind(h)$ like an automorphism of $\str{h}$. This can be determined
%   easily. If no such $h'$ exists halt and output that there is no automorphism
%   extending $\sigma$. Since $C$ has unique labels it has unique extensions,
%   and so there is at most one such $h'$. We thus let $\pi (h) = h'$.

%   This recursive approach can be implemented as an algorithm that runs in time
%   polynomial in the combined size of the inputs and outputs the required
%   automorphism if it exists.
% \end{proof}

\begin{lem}
  There is an algorithm takes as input a $(\BB, \rho)$-circuit $C$ of order $n$
  with unique labels and $\sigma \in \sym_n$ and outputs for each gate $g$ the
  image of $g$ under the action of the unique automorphism extending $\sigma$
  (if it exists). This algorithm runs in time polynomial in the combined size of
  the input circuit and the encoding of the permutation.
  \label{lem:compute-automorphisms}
\end{lem}
\begin{proof}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$. Let $C_\equiv =
  \langle G_\equiv, \Omega_\equiv, \Sigma_\equiv, \Lambda_\equiv, L_\equiv
  \rangle$ be a quotient of $C$. We recursively build up the mapping $\pi' \in
  \aut(C_\equiv)$ extending $\sigma$. If at some point in the recursive
  construction we arrive at a point where no mapping for $g$ can be found we
  halt at that point and return that no automorphism exists.

  Let $h$ be any gate in $C_\equiv$. Suppose $h$ is an input gate. If $h$ is a
  constant gate then let $\pi' (h) = h$. If $h$ is a relational gate such that
  $R := \Sigma_\equiv(h)$, then check if there exists $h'$ such that
  $\Sigma_\equiv (h') = R$ and $\sigma \Lambda_\equiv(h) = \Lambda_\equiv(h')$,
  and also check that either both $h$ and $h'$ are output gates or neither are
  output gates. If no such $h'$ exists then halt and output that no automorphism
  exists. If neither $h$ nor $h'$ are output gates then set $\pi'(h) = h'$. If
  both $h$ and $h'$ are output gates then check if $\sigma \Omega^{-1}_\equiv(h)
  = \Omega^{-1}_\equiv(h')$. If the equality holds set $\pi'(h) = h'$, otherwise
  halt and output that no automorphism exists. We note that, from the definition
  of an automorphism, there is at most once such $h'$ meeting this criteria, and
  so $\pi'(h)$ is well-defined.

  Let $h$ be an internal gate in the circuit and assume we have defined
  $\pi'(g)$ for every gate $g$ of depth less than $h$. Let $h'$ be a gate in the
  circuit such that $\Sigma_\equiv(h) = \Sigma_\equiv (h')$, $\pi' L(h)$ is
  isomorphism-equivalent to $L_\equiv(h')$ and, if $h$ is an output gate then
  $h'$ is an output gate such that $\sigma \Omega^{-1}_\equiv(h) =
  \Omega^{-1}_\equiv(h')$. Suppose there is another gate $h''$ in the circuit
  that meets all of those criteria as well. But then it follows that $h'' \equiv
  h'$. Since $C_\equiv$ is reduced, we then have that $h'' = h'$. We thus have
  that the choice of $h'$, if it exist, is unique. Note that, since $C$ has
  unique labels $C_\equiv$ has unique labels, and so unique extensions, and so
  we have that $\pi' L_\equiv(h)$ is isomorphism-equivalent to $L_\equiv(h')$
  if, and only if, $L_\equiv(h')^{-1}\pi'L_\equiv(h)$ acts on $\ind(h)$ like an
  automorphism of $\str{h}$. This is easy to determine. If no such $h'$ exists,
  halt and output that there is no automorphism extending $\sigma$. Otherwise,
  let $\pi'(h) = h'$.

  It is easy to see that if there is an automorphism of $C_\equiv$ extending
  $\sigma$ then this construction must have been successful and $\pi'$ is the
  unique automorphism of $C_\equiv$ extending $\sigma$. Thus, if we have thus
  far halted and returned that no automorphism exists, then indeed there is no
  automorphism of $C_\equiv$ extending $\sigma$ and so, from
  Lemma~\ref{lem:quotient-circuits-preserve}, no automorphism of $C$ extending
  $\sigma$. We suppose the algorithm has not halted, and thus that $\pi'$ is an
  automorphism of $C_\equiv$ extending $\sigma$.

  We say that a function $\pi : G \rightarrow G$ is a \emph{pseudo-automorphism}
  extending $\sigma$ if (i) $\pi$ acts like an automorphism extending $\sigma$
  on the input and output gates, (ii) $\Sigma (\pi (h)) = \Sigma(h)$ for all $h
  \in G$, (iii) $\pi(h) \in H_{\pi(g)}$ for all $h \in G$ and $g \in W(h,
  \cdot)$, and (iv) $\pi (h) \in \pi'([h])$.

\begin{claim}
  If $\pi$ is an automorphism of $C$ extending $\sigma$ then $\pi$ is a
  psudo-automorphism extending $\sigma$.
\end{claim}
\begin{proof}
  Suppose $\pi$ is an automorphism of $C$ extending $\sigma$. It is easy to see
  that conditions (i), (ii) and (iii) are satisfied. We now show that (iv) is
  satisfied as well. Notice that, since $C_\equiv$ is reduced and so has unique
  extensions, $\pi'$ is the unique automorphism of $C_\equiv$ extending
  $\sigma$. We have from Lemma~\ref{lem:quotient-circuits-preserve} that there
  exists $\pi_\equiv \in \aut(C_\equiv)$ extending $\sigma$ such that
  $\pi_\equiv ([g]) = [\pi(g)]$. It follows that for all $h \in G$, $\pi(h) \in
  \pi_\equiv([h]) = \pi'([h])$.
\end{proof}

We now recursively build up the pseudo-automorphism $\pi$ extending $\sigma$. If
at any point in this construction we assert that an object exists when it does
not, we halt and output that there is no automorphism extending $\sigma$.
Importantly, this construction is defined such that $\pi$, if it exists, is the
\emph{unique} pseudo-automorphism extending $\sigma$.

For each gate $h$ in $C$ let $Q(h)$ be the maximum length of a path from $h$ to
an output gate. Let $h$ be a gate in $C$. Suppose $Q(h) = 0$. Then $h$ is an
output gate. Let $h' \in G$ be such that $h' = \Omega (\sigma \Omega^{-1}(h))$
and $\Sigma (h) = \Sigma (h')$. From the definition of an automorphism if $h'$
exists it is the unique gate satisfying these criteria. We let $\pi (h) = h'$.

Suppose $h$ is a gate in the circuit with $Q(h) > 0$ and for all $g$ such that
$Q(g ) < Q(h)$ we have defined $\pi (g)$. Let $H = \bigcap_{g \in W(h, \cdot)}
H_{\pi(g)}$. If $H$ is empty then we cannot satisfy condition (iii) in the
definition of a pseudo-automorphism, and so we halt and output that no extension
exists. Suppose that $H$ is non-empty. If $h$ is an input gate then there is an
obvious action of $\sigma$ on $h$, and we let $h' = \sigma h$. If $h$ is an
output gate, let $h' \in G$ be such that $h' = \Omega (\sigma \Omega^{-1} (h))$
and $\Sigma (h) = \Sigma (h')$. If $h' \not\in H$ we halt and output that no
extension exists, and otherwise we let $\pi (h) = h'$. Notice that in the case
that $h$ is an output gate or an input gate then from the definition of an
automorphism $h'$ is the unique gate satisfying these criteria. Suppose $h$ is
an internal non-output gate. Let $h_\equiv \in G_\equiv$ be such that $h_\equiv
= [h]$. Let $h' \in \pi_\equiv (h_\equiv)$ be such that $h' \in H$. We now show
that $h'$, if it exists, is the unique gate satisfying these criteria. Let $h''
\in \pi_\equiv (h_\equiv)$ and $h'' \in H$. Then $h'' \equiv h'$ and for all $g
\in W(h, \cdot)$, $h' \in H_g$ and $h'' \in H_g$. But then, since every $g \in
W(h, \cdot)$ has unique labels, $h'' = h'$. Let $\pi (h) = h'$.
